---
title: "Observational correlations between Olink and SomaScan"
author: "Baihan Wang"
date: "2023-04-04"
output: html_document
---

```{r setup, include=FALSE}
library(ggplot2)

rm(list = ls())

setwd("K:/kadoorie/Staff_Folders/BaihanW/proteomics/data")

olink_soma_normal <- read.csv("olink_soma_normal.csv")

olink_soma_non_normal <- read.csv("olink_soma_non_normal.csv")

overlap <- read.csv("overlap.csv")

protein_count <- as.data.frame(table(overlap$uniprot_id))

```

Overall, there are 2,683 Olink-SomaScan protein target pairs for 2,155 unique proteins. Those include 2,155 Olink measures and 2,683 SomaScan reagents. 448 proteins were targeted by more than one SomaScan reagents. The table below shows the number of SomaScan reagents each protein has:

```{r protein count}

table(protein_count$Freq)

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
